---
title: "Assignment 0 Advanced BA"
author: "Cam Holecek"
date: "2025-02-03"
output: html_document
---

```{r}
install.packages("readxl")
install.packages("dplyr") 

library(readxl)
library(dplyr)

```

```{r}
summary(`netflix_titles.(1)`)
```

Length of each variable is 8807 and there is 12 columns

```{r}
str(`netflix_titles.(1)`)

# Get summary statistics
summary(`netflix_titles.(1)`)

# Count missing values
colSums(is.na(`netflix_titles.(1)`))

```

There seems to be 0 missing values in each variable or column. The dataset includes categorical variables such as type (Movie or TV Show), title, director, cast, country, date_added, rating, and listed_in (genres). It also includes numerical data like release year, ranging from 1925 to 2021.

If you want to predict a numerical variable, such as estimating the popularity of a show based on features like release year, country, or genre.
Example: Predicting movie duration based on release_year, rating, or listed_in.
Suitable if: You have a clear dependent variable 


